### 2019-04-11 1_introduction.tex
Apply Pat's comments.

One approach to comparing the performance of different systems is through \emph{proxy-} or
\emph{mini-apps}. Because they distill the structure of a larger
application, mini-apps can provide insight
without the expense of developing a production code. However, despite the name, our experience is that
mini-apps still require significant investment to develop
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop a correct implementation. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Few published studies involve more than a handful of systems~\cite{LULESH13}.

>>>>

One approach to comparing the performance of different systems is through \emph{proxy-} or
\emph{mini-apps}. Because they distill the key computational characteristics of a larger
application, mini-apps can provide insight
without the expense of developing a production code. However, despite the name, our experience is that
mini-apps still require significant investment to develop
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop a correct implementation. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Few published studies involve more than a handful of systems~\cite{LULESH13}.

### 2019-04-11 5_evaluation.tex
Apply Pat's comments.

Most systems for HPC are highly scalable,
but this is not true of all the systems included in this
evaluation. Lower is better in Figure~\ref{fig:metg-compute}, and a
flat line is ideal. Lines that rise with node count indicate less than
ideal scaling. Most notably, Spark is typically
intended for use in industrial data center applications with task
granularities measured in tens of seconds. Spark uses a centralized
controller, which limits throughput, and this is visible in the figure
as the line for Spark immediately rises with node count. Keep in mind also
that Spark is being evaluated here with a non-trivial dependence
pattern which is relatively unrepresentative of Spark's normal use
cases. Spark is more efficient with trivial parallelism, as described
in Section~\ref{subsec:number-of-dependencies}.

>>>>

Most systems for HPC are highly scalable,
but this is not true of all the systems included in this
evaluation. Lower is better in Figure~\ref{fig:metg-compute}, and a
flat line is ideal. Lines that rise with node count indicate less than
ideal scaling. Most notably, Spark is typically
intended for use in industrial data center applications with task
granularities measured in tens of seconds. Spark uses a centralized
controller, which limits throughput, and this is visible in the figure
as the line for Spark immediately rises with node count. Keep in mind
that Spark is being evaluated here with a non-trivial dependence
pattern which is relatively unrepresentative of Spark's normal use
cases. Spark is more efficient with trivial parallelism, as described
in Section~\ref{subsec:number-of-dependencies}.
